Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-05 paper/paper.tex
edit sec 5
Added solution for running example.
revised sec 5 (elements specific to control)

\paragraph{Elements specific to control systems}
There are two different algorithms in DSVerifier that can be used for
stability verification, one based on Schur's decomposition and another
one based on Jury's criteria \cite{DBLP:journals/dafes/BessaICF16};
here, the Jury's method is chosen due to its efficiency.

@@

Next, the following Jury matrix
$M = [m_{ij}]_{(2N−2)\times N}$ is built from $S(z)$ coefficients:
%
$$
M=\left( 
\begin{array}{c}
V^{(0)}\\
V^{(1)}\\
\vdots\\
V^{(N-2)}
\end{array}
\right)
$$
%
where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
%
$$
v_{ij}^{(0)}=\left\{
\begin{array}{ll}
a_{j-1}, & \texttt{if}~i=1\\
v_{(1)(N-j+1)}^{0},&\texttt{if}~i=2
\end{array}
\right.
$$
%
$$
v_{ij}^{(k)}=\left\{
\begin{array}{ll}
0,&\texttt{if}~j>n-k\\
v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \texttt{if}~j\leq n-k ~\texttt{and}~i=1\\
v_{(1)(N-j+1)}^{k},& \texttt{if}~j\leq n-k ~\texttt{and}~i=2\\
\end{array}
\right.
$$
%
where $k \in \mathbb{Z}$, such that $0 < k < N − 2$. 
$S(z)$ is the
characteristic polynomial of a stable system if and only if
the following four propositions hold:
\begin{itemize}
\item $R_1: S(1) > 0$;
\item $R_2: (−1)^N S(−1) > 0$;
\item $R_3: |a_0| < a_N$;
\item $R_4: m_{11} > 0 \equiv m_{31} \wedge m_{51} \wedge \cdots \wedge m_{(2N−3)(1)}$.
\end{itemize}

The stability property is then encoded by creating a
constraint of the form:
$$\phi_{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4)$$
\cdsay{figure out what is existentially quantified for the final $\sigma$.}

>>>>

\paragraph{Elements specific to control systems}
Next, we describe the specific property that we pass to the 
program synthesiser as the specification $\sigma$.
There are two different algorithms in DSVerifier that can be used for
stability verification, one based on Schur's decomposition and another
one based on Jury's criteria \cite{DBLP:journals/dafes/BessaICF16}.
Here, we choose Jury's method due to its efficiency.

@@

Next, the following Jury matrix
$M = [m_{ij}]_{(2N−2)\times N}$ is built from $S(z)$ coefficients:
%
$$
M=\left( 
\begin{array}{c}
V^{(0)}\\
V^{(1)}\\
\vdots\\
V^{(N-2)}
\end{array}
\right)
$$
%
where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
%
$$
v_{ij}^{(0)}=\left\{
\begin{array}{ll}
a_{j-1}, & \texttt{if}~i=1\\
v_{(1)(N-j+1)}^{0},&\texttt{if}~i=2
\end{array}
\right.
$$
%
$$
v_{ij}^{(k)}=\left\{
\begin{array}{ll}
0,&\texttt{if}~j>n-k\\
v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \texttt{if}~j\leq n-k ~\texttt{and}~i=1\\
v_{(1)(N-j+1)}^{k},& \texttt{if}~j\leq n-k ~\texttt{and}~i=2\\
\end{array}
\right.
$$
%
where $k \in \mathbb{Z}$, such that $0 < k < N − 2$. 
$S(z)$ is the
characteristic polynomial of a stable system if and only if
the following four propositions hold:
\begin{itemize}
\item $R_1: S(1) > 0$;
\item $R_2: (−1)^N S(−1) > 0$;
\item $R_3: |a_0| < a_N$;
\item $R_4: m_{11} > 0 \wedge m_{31}>0 \wedge m_{51}>0 \wedge \cdots \wedge m_{(2N{-}3)(1)}>0$.
\end{itemize}

The stability property is then encoded by creating a
constraint of the form:
$$\phi_{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4)$$
%\cdsay{figure out what is existentially quantified for the final $\sigma$.}

In the {\sc verify} phase, if the system is unstable for the current candidate solution,
i.e. if $\neg \phi_{stability}$ is satisfiable for $S(z)$, 
then we obtain a counterexample denoted by 
values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$,
which make the closed-loop system unstable. This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
we obtain a candidate solution consisting 
of a controller $D_C$ and $N_C$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.
